The relative roles of genetic, ecological and environmental factors in species radiations

### 2018-01-16 paper/draft.tex
add to MM
MM edit

Recently, a group of influential island biogeography researchers proposed a set of 50 questions in island biogeography that still need answering (Patiño et al. 2017).
A subset of these questions deals with the topic of speciation and radiations on islands.
Still, the proposed mechanisms so far include only ecological or geo-morphological processes,
while genetic properties are hardly recognized in the island context.
At the same time, an increasing number of studies investigates genetic processes and
their effect on reproductive/ecological isolation of populations (e.g., Via).

@@

\section{Material and Methods}
We use an individual based metacommunity model written in julia \cite{JULIALANG}.
Each individual is characterized by a set of genetically controlled traits and is submitted to processes of
establishment, competition, growth, (density independent) mortality, reproduction and dispersal.
Each of which processes is affected by the individuals' characteristics.
The simulation arena consists of a larger landmass (the mainland) holding an initial pool of evolving populations and a smaller, initially unpopulated island some distance apart.
During the course of the simulation, individuals may disperse from the mainland to the island, thus colonizing it.

@@

\subsection{scenarios}
In the simulations, we modify the value and extent of
(a) gene linkage,
(b) reproductive isolation,
(c) habitat diversity, and
(d) topographical complexity
to asses their relative contribution on community composition.
\Cref{tab:scenarios} summarizes the parameters which were varied for the scenarios, their meaning and their values. %TODO: make table.
For each parameter combination, we launched a number of %TODO: how much?
replicates.

>>>>

Recently, a group of influential island biogeography researchers proposed a set of 50 questions in island biogeography that still need answering (Patiño et al. 2017).
A subset of these questions deals with the topic of speciation and radiations on islands.
Still, the proposed mechanisms so far include only ecological or geo-morphological processes,
while genetic properties are hardly recognized in the island context.
At the same time, an increasing number of studies investigates genetic processes and
their effect on reproductive/ecological isolation of populations (e.g., Via & West 2008, Via 2001 and references therein).

@@

\section{Material and Methods}
We use an individual based metacommunity model written in julia \cite{JULIALANG}.
Each individual is characterized by a set of genetically controlled traits and is submitted to processes of
establishment, competition, growth, (density independent) mortality, reproduction and dispersal.
Each of which process is affected by the individuals' trait characteristics.
The simulation arena consists of a larger landmass (the mainland) holding an initial pool of evolving populations and a smaller, initially unpopulated island some distance apart.
During the course of the simulation, individuals may disperse from the mainland to the island, thus colonizing it.
The complete state of the simulation is recorded every 1000 time steps for analysis.

@@

\subsection{scenarios}
In the simulations, we modify the value and extent of
(a) gene linkage,
(b) reproductive isolation,
(c) habitat diversity, and
(d) topographical complexity
to asses their relative contribution on community composition.
\Cref{tab:scenarios} summarizes the parameters which were varied for the scenarios, their meaning and their values. %TODO: make table.
Each parameter combination replicated %TODO: how much?
times.
